---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# orobrs

<!-- badges: start -->
[![R-CMD-check](https://github.com/asshah4/orobrs/workflows/R-CMD-check/badge.svg)](https://github.com/asshah4/orobrs/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/asshah4/orobrs/branch/main/graph/badge.svg)](https://codecov.io/gh/asshah4/orobrs?branch=main)
<!-- badges: end -->

The goal of `orobrs` is to handle cyclical events, of both continuous and categorical data. The name stems from the Hellenic tradition of perpetual and rhythmic cycles of time - instead of linear time. Sometimes seen with the symbol of the _ouroboros_, of the snake eating its tail, _Aion is the god of the cyclic ages_.

## Installation

Once it is available, you can install the released version of `orobrs` from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
#install.packages("orobrs")
```

And the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("asshah4/orobrs")
```
